Viscous Transport in Eroding Porous Media

### 2019-10-03 docs/transport/erosion_transport.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
As a continuation of our previous work~\cite{qua-moo2018}, we have
simulated dense suspensions and characterized transport in viscous
erosion of porous media. A BIE formulation is used to solve the Stokes
equations and to compute the shear stress. However, to simulate
nearly-touching grains and to consider transport, it is necessary to
integrate near-singular functions. This is achieved by extending a
Barycentric quadrature rule~\cite{bar-wu-vee2015} to accurately compute
the erosion rate and vorticity. By using this quadrature rule, we are
able to form stable simulations of erosion with $N = \mathcal{O}(100)$
discretization points, while the trapezoid rule would require
$\mathcal{O}(10^5)$ discretization points.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
As a continuation of our previous work~\cite{qua-moo2018}, we have
simulated dense suspensions and characterized transport in viscous
erosion of porous media. A BIE formulation is used to solve the Stokes
equations and to compute the shear stress. However, to simulate
nearly-touching grains and to consider transport, it is necessary to
integrate near-singular functions. This is achieved by extending a
Barycentric quadrature rule~\cite{bar-wu-vee2015} to accurately compute
the erosion rate and vorticity. By using this quadrature rule, we are
able to \nick{per}form stable simulations of erosion with $N = \mathcal{O}(100)$
discretization points, while the trapezoid rule would require
$\mathcal{O}(10^5)$ discretization points.
